
---
title: 'Graph 3: PCA Correlations '
author: ''
date: '2018-06-12'
slug: graph-4-tba
categories: []
tags: []
description: Desc
hacker_news_id: ''
lobsters_id: ''
meta_img: /images/image.jpg
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) 
library(ggplot2)
#library(ggalt)
library(ggradar)
library(extrafont)
library(ggfortify)
library(infer)
library(forcats)
library(ggridges)
library(here)
library(scales)
library(reshape2)

library(viridis)
library(shiny)
```



## Preliminaries
## Data

All the graphs of this series are generated from data concerning frequency with which words from assorted dictionaries appear in original reddit posts from various subreddits. 

Because `alldicts` is of such high dimensionality-- 65 is a lot of features to keep track of-- I ran principle component analysis (PCA) on the data to reduce the dimensionality to 21 features, while still explaining 90% of the variance within the dataset. The draw back of this approach is that the principle components can be difficult to interpret. Thus, the plots below explore the relationship/correlation between each of these the 21 principle components a the original 65 features. 

```{r}
# original data
nfreqs <- read_csv(here('static','data','redditProject','normal_subset_freqs.csv'))
# data in PCA space
redfreqs <- read_csv(here('static','data','redditProject','reduced_normal_subset_freqs'))

#Orininal dimensionality, # of principle components used
od_num=65
pc_num=21

# Calculate correlation
correlations <- cor(nfreqs[c(2:(od_num+1))],redfreqs[c(2:(pc_num+1))])

#Tidyify
corlong <- melt(correlations ) %>% 
   setNames(c('orig', 'red_dim', 'correlation'))

```


### Audience

In its current form, audience for this project is almost entirely myself and the professors I'm trying to convince to help me with this project. Eventually I hope to research may be of interest to a larger group, including: 

1. Linguists interested in this method of textual analysis and the language of internet forums
1. Computer sciencists interested in the distributed computing or machine learning that went into this project
1. Social scientists studying any of the many social groups involved on reddit. 

## Plot Type: Tiled Correlations

### How to read it and what to look for 

### Presentation Tips

### Variations and Alternatives


## Plot Description

### Representaton 
```{r}
ggplot(corlong, aes(x=red_dim, y=orig, fill=correlation))+
  geom_tile()+ 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  scale_fill_distiller(palette = "PRGn")
  #scale_fill_viridis(option='E')

```


### Methods

```{r}
covariances <- read_csv(here('static','data','redditProject','subset_covariance.csv'))
covlong <- gather(covariances, key=newDimension, value=covariance, -X1)

ggplot(covlong, aes(x=newDimension, y=X1, fill=covariance))+
  geom_tile()+
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

