---
title: 'Graph 4: Radar'
author: ''
date: '2018-06-13'
slug: graph-3-tba
categories: []
tags: []
description: Desc
hacker_news_id: ''
lobsters_id: ''
meta_img: /images/image.jpg 
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) 
library(ggplot2)
#library(ggalt)
library(ggradar)
library(extrafont)
library(ggfortify)
library(infer)
library(forcats)
library(ggridges)
library(here)
library(scales)
```

## Preliminaries
### Data

All the graphs of this series are generated from data concerning frequency with which words from assorted dictionaries appear in original reddit posts from various subreddits. This graph shows clusters centers generated by running K means clustering (K=7) on the data shown in `alldicts` in [graph 2](/post/2018-06-11-graph-2-raincloud/), after reducing its dimensionality through prinicipal component analyis to the 21 dimensions shown in [graph 3](/post/graph-3-tba/)

### Audience


1. Linguists interested in this method of textual analysis and the language of internet forums
1. Computer sciencists interested in the distributed computing or machine learning that went into this project
1. Social scientists studying any of the many social groups involved on reddit. 


## Plot Type: Radar

### How to read it and what to look for 

### Presentation Tips

### Variations and Alternatives


## Plot Description

### Representaton 

### Methods

```{r, fig.height=7, fig.width=10 }
radar_colour=rep(c("#FF5A5F", "#FFB400", "#007A87",  "#8CE071", "#7B0051", 
                       "#00D1C1", "#FFAA91", "#B4A76C", "#9CA299", "#565A5C", "#00A04B", "#E54C20"), 100)

clusters <- read_csv(here('static','data','redditProject','centers')) 

clusters <- clusters %>%  
  mutate_at(vars(starts_with('d')),rescale)
clusters
 
dlabels= c('d1 ~negative', 'd2 ~bio', 'd3 ~feelings', 'd4 ~social, not feelings', 
           'd5 ~pos emote, no functional','d6 ~physics and bio','d7 ~sensing',
           'd8 ~leisure not money', 'd9 ~swearing and money, no bio',
           'd10 ~certain absolutist',
           'd11 ~work, num, no sensing',
           'd12 ~inhibition, sex, no money',
           'd13 ~home, hearing',
           'd14 ~work, acheive, no swearing',
           'd15 ~2nd person, no friends',
           'd16 ~cause, acheive, no death',
           'd17 ~friends',
           'd18 ~family',
           'd19 ~ingest',
           'd20 ~2nd person, num',
           'd21 ~home, death, no religion'
           )

ggradar(clusters[1,], grid.label.size = 5,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour)+ 
  ggtitle("point1")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[2,], grid.label.size = 5,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[2])+
  ggtitle("point2")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 

ggradar(clusters[3,],grid.label.size = 5,
        group.point.size = 3,
        axis.label.size = 4,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[3])+
  ggtitle("point3")+ 
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[4,], grid.label.size = 5,
        group.point.size = 3,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[4])+
  ggtitle("point4")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[5,], grid.label.size = 5,
        group.point.size = 3,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 11,
        group.colours = radar_colour[5])+
  ggtitle("point5")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 

          
          
ggradar(clusters[6,], grid.label.size = 5,
        group.point.size = 4,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 9, 
        group.colours = radar_colour[6])+
  ggtitle("point6")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


ggradar(clusters[7,], grid.label.size = 5,
        group.point.size = 4,
        axis.label.size = 3,
        axis.labels = dlabels,
        legend.text.size = 9,
        group.colours = radar_colour[7])+
  ggtitle("point7")+
  theme(legend.position="bottom") + 
  theme(text=element_text(family='Lato')) 


radar <- ggradar(clusters, 
                 font.radar = 'Lato', 
                 grid.label.size = 0,
                 group.point.size = 3,
                 axis.label.size = 3,
                 axis.labels = dlabels,
                 legend.text.size = 6,
                 plot.extent.x.sf = 2
                 )+
  ggtitle("7 cluster centers in 11 dimensions")+
  theme(legend.position="right") + 
  theme(text=element_text(family='Lato'))


radar
```
